Exploring Rural Shrink Smart Through Guided Discovery Dashboards

### 2021-12-08 SCCAbstract_SDSS2022-knitr.Rnw
Updating the folder with useful files with name changes

% File SDSS2020_SampleExtendedAbstract.tex
\documentclass[10pt]{article}
\usepackage{sdss2020} % Uses Times Roman font (either newtx or times package)
\usepackage{url}
\usepackage{latexsym}
\usepackage{amsmath, amsthm, amsfonts}
\usepackage{algorithm, algorithmic}  
\usepackage{graphicx}

\title{Symposium on Data Science and Statistics (SDSS 2022) \\
Submission and Formatting Instructions for Extended Abstracts}

@@

\begin{document}

@@

{\bf Keywords:} Interactive Dashboards, Exploratory Data Analysis (EDA), Design Space(??)

<<setup, include = F>>=
# This is a code chunk
@

@@

\section{Data Description}
Using an exploratory methodology, we collected open source data from the Iowa Data Gov website to understand the

we derived a design space consisting of 3-4 visual and functional aspects of dashboards with statistical exploratory data analysis. see Section~\ref{info-on-sections}.

\subsection{Challenges}
While data

The intended use of a dashboard for a novice user drives the choices in the visual and functional design allowances. The factors here capture the roles of each dashboard in the process of analysis and communication. We find that the purpose of a dashboard has been substantially expanded from the operational dashboard to capture decision-making at higher levels, and may not be supportive in decision-making.

{\bf Decision Support} (Strategic, Tactical, Operational): The decision support dimension reflects on the sorts of actionable decisions that dashboards are designed to support.

{\bf Communication and Learning:} We encountered several examples of dashboards that did not solicit decision-making on any temporal scale.

\subsection{Audience}
The visual and functional aspects of our dashboards typically reflect the intended audience, which has a wide-range of characteristics in their domain and visualization aspects of a dashboard and their experience with data.

\section{Related Work}
From previous research has explained how visual analytics addresses the issue of information overload and enables analysts to transform raw data into salient information and knowledge

\section{Data/Results}

We encourage the selective use of tables and/or figures as appropriate.

\subsection{Graphics and Tables}

Place figures and tables in the
paper near where they are first discussed, rather than at the end, if
possible.  It is acceptable that wide illustrations
may run across both columns.  The use of color
is allowed in extended abstract graphics.

\section{Discussion/Conclusions}

\subsection{Appendices and acknowledgements}

Please avoid the use of appendices and acknowledgements 
as separate sections.  Any pertinent material should be included in the
body of the extended abstract rather than in an appendix.  If 
acknowledgements are necessary then they should be made using footnotes.

If you wish to provide links to accompanying code, this is allowable because
SDSS encourages best practices for reproducible research.  However, all
conclusions and exposition relevant to the refereeing process should appear in
the body of the extended abstract; furthermore, we cannot guarantee that 
code will be checked or even consulted during the refereeing process.

\subsection{Refereeing Decisions}
It is expected that accepted papers will be presented in person at SDSS in Pittsburgh 
from June 4 to 6, 2020.
Accepted papers' authors will be notified in plenty of time to make registration and travel 
arrangements and for papers not accepted to submit an e-poster to the 
conference if they so choose.

>>>>

% File SDSS2020_SampleExtendedAbstract.tex
\documentclass[10pt]{article}
\usepackage{newtxtext, newtxmath, times}
\usepackage{sdss2020} % Uses Times Roman font (either newtx or times package)
\usepackage{url}
\usepackage{latexsym}
\usepackage{amsmath, amsthm, amsfonts}
\usepackage{algorithm, algorithmic}  
\usepackage{graphicx}

%\title{Symposium on Data Science and Statistics (SDSS 2022) \\
%Submission and Formatting Instructions for Extended Abstracts}

\title{Exploring Rural Shrink Smart Through Guided Discovery Dashboards}

@@

\begin{document}
\SweaveOpts{concordance=TRUE}

<<setup, include=FALSE, cache = FALSE>>=
library(knitr)
opts_chunk$set(
concordance=TRUE
)
@

@@

{\bf Keywords:} Interactive Dashboards, Exploratory Data Analysis (EDA), Design Space, Guided Discovery

@@

\section{Data Collection}
Iowa Data were used to create the SCC dashboard. Iowa Data is a public data website that collects and updates data on the State of Iowa Government, data are mostly on a town/city level that is not collected in National Data Collection Systems. Iowa Data website is a unique and detailed database of information about residents, such as liquor sales and school building locations. For the purpose of the Rural Shrink Smart Dashboard, we will collect as much data as possible, such as obtaining fire department and hospital details. These data are collected on all towns that are available. We will use statistical clustering methods will be used to determine the town classifications to help improve the rural towns.

\section{Data Challenges}
Iowa Data website has an exhaustive and detailed data, but that data collected has missing information. This information can be broken down into two separate types, in which we will call a true missing, a particular service that is missing because the town does not have or offer the service to the community. For example, many small towns do not have a hospital that will only cater to the community, but they will have access to a hospital in a neighboring town. The second type of missing data are when data should be available and are not currently being collected in the data but are available in a different data source. For example, our public school data does not actual represent public schools in bigger cities, suggesting that the closest Elementary school is 20 miles away, which we understood that to be untrue. This type of missing data is very typical in data collection, but could led our research in a poor direction.

\section{Guiding Design Principles}
Dashboards have a variety of challenges, our research will focus on users' challenges with understanding data and statistical relationships of dashboards. We investigate user interaction strategies that will not challenge the knowledge of the analyst in a variety of backgrounds. With little research on the adaptation of dashboards, we will particularly focus on the techniques that to solve interaction and information presentation challenges. In our research, we would like to use a guiding design principles to develop and design the following:
\begin{itemize}
\item Showing a town analyst with peers to help with changes that improved the QoL
\item Dashboard design that will make the town the main focus without distracting the analysts with peer comparisons
\item Creating a feedback loop that will, assist in the guided discovery from the analysts
\end{itemize}

\section{Current Progress and Future Work}

\subsection{Current Progress}
Our research as stated above, we would like to produce and develop a guided discovery dashboard that will allow rural analysts the ability to access information that will help with the Quality of Life in their town. This dashboard will be used to help the analyst make data-driven decisions about making effective changes in their communities. Our dashboard will be used to 
\subsection{Future Work}

\section{Acknowledgements}
We would like to thank our sponsors and grant provider NSF, LSAMP Inspire Program and Iowa League of Cities. We would like to thank our partners and team members at Iowa State University and University of Nebraska - Lincoln. We would like to thank the State of Iowa for providing Data along with our partners in the Rural Iowa communities.

### 2021-12-08 SCCAbstract_SDSS2022-knitr.tex
Updating the folder with useful files with name changes

\begin{document}
\SweaveOpts{concordance=TRUE}

<<setup, include=FALSE, cache = FALSE>>=
library(knitr)
opts_chunk$set(
concordance=TRUE
)
@

@@

\section{Data Collection}
Iowa Data were used to create the SCC dashboard. Iowa Data is a public data website that collects and updates data on the State of Iowa Government, data are mostly on a town/city level that is not collected in National Data Collection Systems. Iowa Data website is a unique and detailed database of information about residents, such as liquor sales and school building locations. For the purpose of the Rural Shrink Smart Dashboard, we will collect as much data as possible, such as obtaining fire department and hospital details. These data are collected on all towns that are available. We will use statistical clustering methods will be used to determine the town classifications to help improve the rural towns.

\section{Data Challenges}
Iowa Data website has an exhaustive and detailed data, but that data collected has missing information. This information can be broken down into two separate types, in which we will call a true missing, a particular service that is missing because the town does not have or offer the service to the community. For example, many small towns do not have a hospital that will only cater to the community, but they will have access to a hospital in a neighboring town. The second type of missing data are when data should be available and are not currently being collected in the data but are available in a different data source. For example, our public school data does not actual represent public schools in bigger cities, suggesting that the closest Elementary school is 20 miles away, which we understood that to be untrue. This type of missing data is very typical in data collection, but could led our research in a poor direction.

@@

\section{Current Progress and Future Work}

\subsection{Current Progress}
Our research as stated above, we would like to produce and develop a guided discovery dashboard that will allow rural analysts the ability to access information that will help with the Quality of Life in their town. This dashboard will be used to help the analyst make data-driven decisions about making effective changes in their communities. Our dashboard will be used to 
\subsection{Future Work}

\section{Acknowledgements}
We would like to thank our sponsors and grant provider NSF, LSAMP Inspire Program and Iowa League of Cities. We would like to thank our partners and team members at Iowa State University and University of Nebraska - Lincoln. We would like to thank the State of Iowa for providing Data along with our partners in the Rural Iowa communities.

>>>>

\usepackage{Sweave}
\begin{document}
\input{SCCAbstract_SDSS2022-knitr-concordance}

\begin{Schunk}
\begin{Sinput}
> library(knitr)
> opts_chunk$set(
+ concordance=TRUE
+ )
\end{Sinput}
\end{Schunk}

@@

\section{Data Collection}
Iowa Data Gov data were used to create the SCC dashboard. Iowa Data Gov is a public data website that collects and updates data on the state of Iowa, data are mostly on a town/city level that is not collected in National Data Collection Systems. Iowa Data Gov website is a unique and detailed database of information about residents, such as liquor sales and school building locations. For the purpose of the Rural Shrink Smart Dashboard, we will collect as much data as possible, such as obtaining fire department and hospital details. These data are collected on all towns that are available. We will use statistical clustering methods will be used to determine the town classifications to help improve the rural towns.

\section{Data Challenges}
Iowa Data Gov website has an exhaustive and detailed data, but that data collected has missing information. This information can be broken down into two separate types, in which we will call a true missing, a particular service that is missing because the town does not have or offer the service to the community. For example, many small towns do not have a hospital that will only cater to the community, but they will have access to a hospital in a neighboring town. The second type of missing data are when data should be available and are not currently being collected in the data but are available in a different data source. For example, our public school data does not actual represent public schools in bigger cities, suggesting that the closest Elementary school is 20 miles away, which we understood that to be untrue. This type of missing data is very typical in data collection, but could led our research in a poor direction.

@@

\section{Current Work/ Future Work}

We encourage the selective use of tables and/or figures as appropriate.

\section{Discussion/Conclusions}

\subsection{Appendices and acknowledgements}

Please avoid the use of appendices and acknowledgements 
as separate sections.  Any pertinent material should be included in the
body of the extended abstract rather than in an appendix.  If 
acknowledgements are necessary then they should be made using footnotes.

If you wish to provide links to accompanying code, this is allowable because
SDSS encourages best practices for reproducible research.  However, all
conclusions and exposition relevant to the refereeing process should appear in
the body of the extended abstract; furthermore, we cannot guarantee that 
code will be checked or even consulted during the refereeing process.

\subsection{Refereeing Decisions}
It is expected that accepted papers will be presented in person at SDSS in Pittsburgh 
from June 4 to 6, 2020.
Accepted papers' authors will be notified in plenty of time to make registration and travel 
arrangements and for papers not accepted to submit an e-poster to the 
conference if they so choose.
